\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{dirtytalk}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\newcommand{\RomanNumeralCaps}[1]
    {\MakeUppercase{\romannumeral #1}}
\name{Bob Guo} %name
\address{1570 Woods Rd, Apt106,Winston-salem,NC} %address
\address{336-473-1796 \\ guoj1995@gmail.com} %phone number and email
\address{https://github.com/BobGuo-1995?tab=repositories}

\begin{document}    
\begin{rSection}{Education}
{\bf Wake Forest University(Top 30)} \hfill {\em August 2015 - May 2019} 
\\ Bachelor of Science,Computer Science.
\end{rSection}
\begin{rSection}{Carrier Objective}
 To work for an organization, which provides me the opportunity to improve my skills and knowledge to grow along with the organization objective.Also,help and contribute to the team to deliver the objective on time. 
\end{rSection}
\begin{rSection}{Projects}
{\bf Pascal-like Compiler in \verb!C++!}\\ This project uses \verb!C++! under the hood to read in and compile Pascal-like syntax language.It provides me with extensive practice in common data structures and solve complex logic of a compiler.Finished the project perfectly, with comment \say{the most perfect project in the class} from the instructor. \\
\\{\bf Course Registration Website}
\\ The project aims to learn a new language fast and able to deliver an up and running project at certain milestone. I am in charge of using \verb!PHP! to develop a front-end to interact with the database and deliver the user story on time. I learned how to adapt to the user expectations and compromise some in order to deliver a final product. The project was a success, and in the final evaluation by the teammate was \say{easy and preferable to work with}. \\
\\{\bf Simple Parallel Cashier System}
\\With the appearance of more and more powerful hardware, we need to learn and adapt to this trend by using the potential provided by the hardware to us.This project simulates real life grocery store check-out: Check for discount, promo code,number of item purchased, and return a total price. Under the hood, it is written in \verb!C++! using MPI. 
\end{rSection}
\begin{rSection}{Skills}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Language(Proficient) \ & \verb!C++!,\verb!C!,\verb!Java! \\
Language(Intermediate)\ & \verb!PHP!,\verb!Javascript! \\
Software \& Tools & MS Office, Latex, Visual Studio, Visual Studio Code \\
Software \& Tools & Terminal,Intellj IDE product, and other most known compiler\\
OS\ &Linux,Windows,Mac OS 
\end{tabular}
\end{rSection}
\begin{rSection}{Work Experience}
\begin{rSubsection}{Nanjing O’Happure Tech Co., Ltd.}{2017/6$-$2017/8}{Software Engineer}{}
\item Work as an itern and help developing new features for an out-dated company website.
\item Use WordPress to develop a front end and also learned other static language like JavaScript and HTML,which help further my understanding in the development of the front end. 
\item Use dynamic language like PHP to work with WordPress plugins and use PHP to work with the SQL database.
\item Learn about the basics of the database,which helps me to work with it using PHP.
\item Earn the title: Best Intern of Summer 2016.
\end{rSubsection}
\begin{rSubsection}{Nanjing O’Happure Tech Co., Ltd.}{2018/6$-$2018/8}{Software Engineer}{}
\item Intern for the tech team and volunteer for the research team 
\item Help with the project \say{Fresh Water,Rural China}
\item Update the old water quality database to better adjust the company products.
\item Successfully complete a simple demo, which can access the database to select the ID, province corresponding to the right water quality.
\end{rSubsection}
\end{rSection}
\begin{rSection}{Academic Achievements}
TEM 8 certification $-$ March.2015
\item Certificate of Shanghai Interpretation Accreditation Test $-$ Dec.2014
\item CET4$-$ Dec. 2014
\item CET6$-$ June. 2015
\item Cambridge English Language Assessment, Business English Certificate Higher $-$May. 2015
\end{rSection}
\newpage
\begin{rSection}{Courses}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
CSC 111-\verb!Java!\ & \say{Wheels of fortune},\say{Black Jack}\\&\say{Connect Four},\say{Connect Four-GUI}\\

\\CSC 112-\verb!C++!\ & \say{Pig Latin},\say{Normalization},\say{Grade Calculator} \\& other projects\\

\\CSC 221-Data Structures\&Algorithm I &  \say{3-D Array},\say{Doubly Linked Lists},\say{Binary Search Tree}\\&\say{Heap},\say{Hash Table},\say{Huffman Code},\say{Page Rank}\\&\say{SudokuBoard} \\

\\CSC 211-Computer Organization\ &Assembly language, Hardware aspect of Computer Science\\

\\CSC 222-Data Structures\&Algorithm \RomanNumeralCaps{2} & \say{RSA}\\ &\say{Matrix Multiplication \& Facebook Search Algorithm} \\& \say{Memory Saving On Knapsack Problem}\\

\\CSC 231-Programming Languages\ & A comparative study of programming language paradigms, \\&including imperative languages, functional programming, \\&logic programming, and object-oriented programming. \\&Syntax, semantics, parsing, grammars, and issues of \\&language design are covered. \\
\\CSC 241-Computer Systems\ & Learn about the OS manage resources and provide an\\& interface between the hardware and the user.\\ & \say{Simple Shell} ,\say{Sleeping Barber},\say{Conway's Problem}\\& \say{Unisex Bathroom},\say{Scheduling Method}\\
\\CSC 331-Software Engineering\ &An introduction to software engineering, the engineering \\&discipline concerned with finding and applying solutions\\& to problems encountered in delivering high quality, \\& large-scale, real-world software systems in a timely and \\ &cost-effective manner.\\
\\CSC 333-Principles of Transalators\ & Study of techniques for translating high-level programming \\&languages to a target language. Typical target languages \\&include Java bytecode and assembly language. Topics \\&include lexical analysis, parsing, intermediate \\&representations, language semantics, code generation, \\&and optimization.\\
\\CSC 346-Parallel Computation \ &Study of techniques for parallel and high performance\\& computing.
\\&  OpenMP,MPI and Pthread Library.\\
\\CSC 355-Intro to Numerical Methods\ & Numerical computations on modern computer architectures;\\& floating-point arithmetic and round-off error. 

\end{tabular}
\end{rSection}
\begin{center}
    Written in Latex.
    \\For the project,you can refer to the Github link at the beginning of the Resume.
    \\Thanks for reading my resume and I am looking forward to work together in the future. 
\end{center}
\end{document}
